Blue Hunters: Bluetooth RSSI Locator Robots

### 2018-02-06 article/article.tex
add average convergence table
More footnotes removed

  The firmware file came from the Arduino forum post. \footnote{The firmware file can be found here:  \url{http://forum.arduino.cc/index.php?action=dlattach;topic=393655.0;attach=183702}}
\end{enumerate}

@@

>>>>

  The firmware file came from the Arduino forum post. \cite{firmwarefile}
\end{enumerate}

@@

\begin{table}[]
\centering
\ra{1.3}
\caption{Average convergence behavior}
\label{table:averagecon}
\begin{tabular}{@{}lll@{}}
\toprule
                       & Robot 0        & Robot 1     \\ \midrule
Convergence time (s)   & 146            & 115         \\
Convergence rate       & 60 \%          & 100 \%      \\
Final distance (cm)    & 35             & 27          \\
Failure distance (cm)  & 308            & --          \\ \bottomrule
\end{tabular}
\end{table}
